Quantifying the global film festival circuit: networks, diversity and value creation

### 2023-02-15 cudan/paperplots.qmd
news

@@

{ggplot(hm , 
       aes(fromlibelle, tolibelle, fill=fillweight, text=tool))+
  coord_cartesian(expand=F)+
  geom_tile(size=0)+
  geom_text(aes(label=toyear, x=0), data=hmy, size=2, hjust=0,vjust=1, angle=90)+
  geom_text(aes(label=toyear,x=fromlibelle, y=0), data=hmy, size=2, vjust=0)+
  #scale_fill_viridis_c(end=0.9, na.value = "white")+
    scale_fill_gradientn(colors = cls, na.value = "white")+
  theme_bw()+
    theme(legend.position = 'none', 
      panel.border = element_blank(),
      panel.grid.minor.x = element_blank(),
      plot.background = element_rect(color="white", fill="white"),
      axis.title = element_blank(),
      axis.text = element_blank(), # element_text(size=3),
      axis.ticks = element_blank()
     # axis.text.x = element_text(angle=90, hjust=1, vjust=1)
    )} %>% ggplotly(tooltip = "text")

@@

# 110
fesfilm2 %>% 
  filter(LibelleEvent_NEW_VZ %in% "Tallinn_Black_Nights_IFF_2012") %>% 
  left_join(filmgen, by="refFilm") %>% 
  count(txtKind) %>% 
  ggplot(aes(y=txtKind, x=n))+
  geom_bar(stat="identity")+
  theme_bw()+
  theme(axis.title = element_blank())+
  coord_cartesian(expand=0)+
  labs(subtitle="Tallinn_Black_Nights_IFF_2012")

@@

>>>>

# big force directed
gr = as_tbl_graph(graph_from_data_frame(e2, directed = F, vertices = nodelist %>% filter(EventID_VZ %in% c(e2$from,e2$to))))
g = ggraph(gr  ) +
  geom_node_point(aes(color=YearEvent, size=nf)) +
  #geom_node_text(aes(label=name)) +
  geom_edge_arc(aes(color=coloryear, alpha=dist),  width=0.1, strength=0.04) +
  scale_color_viridis(end=0.9)+
  scale_edge_color_viridis(end=0.9)+
  scale_edge_alpha(range=c(0.15, 0.5))+
  scale_size(0.5, 1.5)+
  theme_void()+
  theme(legend.position = 'none',
        plot.background = element_rect(color="white", fill="white")
  )

ggsave("yearnetwork2.png", g, width=5000, height=5000, scale=0.6, units="px")
# write_csv(e2, "edgelist_nov22.csv")

@@

{ggplot(hm , 
       aes(fromlibelle, tolibelle, fill=weight, text=tool))+
  coord_cartesian(expand=F)+
  geom_tile(size=0)+
  geom_text(aes(label=toyear, x=0), data=hmy, size=2, hjust=0,vjust=1, angle=90)+
  geom_text(aes(label=toyear,x=fromlibelle, y=0), data=hmy, size=2, vjust=0)+
  #scale_fill_viridis_c(end=0.9, na.value = "white")+
    scale_fill_gradientn(colors = cls, na.value = "white", trans="log10", name="log\nstrength")+
  theme_bw()+
    theme(legend.position = 'none', 
      panel.border = element_blank(),
      panel.grid.minor.x = element_blank(),
      plot.background = element_rect(color="white", fill="white"),
      axis.title = element_blank(),
      axis.text = element_blank(), # element_text(size=3),
      axis.ticks = element_blank()
     # axis.text.x = element_text(angle=90, hjust=1, vjust=1)
    )} %>% ggplotly(tooltip = "text")

# static
ggplot(hm , 
       aes(fromlibelle, tolibelle, fill=weight, text=tool))+
  coord_cartesian(expand=F)+
  geom_tile(size=0)+
  geom_text(aes(label=toyear, x=0), data=hmy, hjust=0,vjust=1, angle=90,size=3, 
            color=viridis_pal(end = 0.9)(13))+
  geom_text(aes(label=toyear,x=fromlibelle, y=0), data=hmy,vjust=0, size=3, 
            color=viridis_pal(end = 0.9)(13))+
  #scale_fill_viridis_c(end=0.9, na.value = "white")+
  #scale_fill_gradientn(colors = cls, na.value = "white", trans="log10", name="log\nstrength")+
  scale_fill_viridis_c(direction=-1,na.value = "white", option="magma", trans="log10", name="log\nstrength")+
  theme_bw()+
    theme(legend.position = c(0.9,0.3), 
      panel.border = element_blank(),
      panel.grid.minor.x = element_blank(),
      plot.background = element_rect(color="white", fill="white"),
      axis.title = element_blank(),
      axis.text = element_blank(), # element_text(size=3),
      axis.ticks = element_blank()
    )

@@

tops = attr(festgenrevecs, "tops") %>% 
  left_join(festgenrevecs %>% filter(!duplicated(EventID_VZ)), by="EventID_VZ") %>% 
  select(txtKind, s, EventID_VZ, libelleFestival_NEW_VZ, YearEvent, LibelleEvent_NEW_VZ) %>% 
  filter(libelleFestival_NEW_VZ %in% exgenfests) %>% 
  filter(YearEvent==2019) %>% 
  ungroup() %>% 
  mutate(colorgenre=case_when(txtKind%in% levels(festgenrevecs$colorgenre)~txtKind, T~"...")) %>% 
  mutate(colorgenre2=fct_relevel(as.factor(colorgenre), 
                                levels(festgenrevecs$colorgenre) %>% gsub("other","...",.)))

ggplot(tops, aes(x=colorgenre2, y=s, fill=colorgenre2))+
  geom_bar(stat="identity", width=1, color=NA)+
  scale_fill_manual(values=sixgcols)+
  #coord_cartesian(expand = 0, ylim=c(0,100))+
  theme_void()+
  theme(axis.title = element_blank(),
        legend.position = "none",
        panel.border  = element_rect(size=0.5, color="gray10", fill=NA)
        )+
  facet_wrap(~libelleFestival_NEW_VZ, strip.position="bottom", scales = "free", nrow=2)

@@

ggplot(attr(genlat, "latmap"), aes(V1,V2,label=txtKind,size=n))+geom_text()+
  scale_size(range=c(1.5,5))+
  theme_void()+
  theme(legend.position = "none",
        panel.border = element_rect(fill=NA)
        )

ggplot( mapping=aes(V1, V2, color=colorgenre))+
  geom_point(aes(shape=ab, text=tool), data=ugenre %>% filter(type=="festival"), size=1, fill=NA, alpha=0.3, shape=16)+
  geom_point(aes(fill=colorgenre, text=tool), data=ugenre %>% 
               filter(type=="festival", event %in% tops$LibelleEvent_NEW_VZ), 
             size=4,  alpha=1, shape=21, color="black")+
  geom_text_repel(aes(label=event %>% gsub("_", "",.)), data=ugenre %>% filter(type=="festival", event %in% tops$LibelleEvent_NEW_VZ), 
            size=4,  alpha=1, hjust=1.1, bg.color="white")+
  #geom_point( data=ugenre %>% filter(type=="film") %>% slice_sample(n = 3), size=0.1, fill=NA,show.legend = FALSE)+
  geom_text_repel(aes(label=event, size=log(sizegen+100)), 
                  data=rbind(
                    ugenre %>% filter(type %in% c("genre")) %>% arrange(-sizegen) %>% head(6),
                    ugenre %>% filter(type %in% c("film")) %>% group_by(colorgenre) %>% 
                      slice(1) %>% head(4)
                  )
                    , 
            lineheight=0.6,
            alpha=1, hjust=0, 
            bg.color="white",  
            show.legend = FALSE, max.overlaps=100, box.padding = 0, point.padding = 0, min.segment.length = 999, force_pull=0.5, max.time = 2)+

  scale_size(range=c(2.5,6), guide="none")+
  scale_color_manual(values=sixgcols, name="")+
  scale_fill_manual(values=sixgcols, name="")+
  theme_void()+
  theme(#legend.position = 'none',
        plot.background = element_rect( fill="white"),
        legend.position = "none"
  )+
  NULL
